An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
change main and rangefilter_legend

	\noindent\textbf{\underline{Puck \cite{puck}.}}  
	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints. In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.

@@

		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.94\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径

@@

	\textit{\textbf{Peak memory usage.}}
	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage. This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.

@@

	\subsection{Range Filtering}

	\subsubsection{Time and Space overhead of index construction.}
	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}

		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

		\vspace{0.3cm}

		% 三图横排
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors. With a smaller range, fewer points remain after filtering, resulting in lower computational cost. In addition, the performance of Faiss is influenced by data dimensionality; it tends to work better on low-dimensional datasets.

>>>>

	\noindent\textbf{\underline{Puck \cite{puck}.}}  
	While simultaneous filtering performs well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints. In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.

@@

		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{16pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.92\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径

@@

	\textit{\textbf{Peak memory usage.}}
	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage. This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms. Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.

@@

	\subsection{Range Filtering}
	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
	\subsubsection{Time and Space overhead of index construction.}

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.93\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

		%\vspace{0.1cm}

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_ndex_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. Faiss does not include optimizations specifically tailored for range filtering scenarios; its query mechanism is identical to that used in tag filtering scenarios. However, since attributes are pre-sorted in range filtering scenarios, the filtering overhead is minimal, leading to improved query performance. Similar to the selectivity observed in attribute filtering, Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors. With a smaller range, fewer points remain after filtering, resulting in lower computational cost. In addition, the performance of Faiss is influenced by data dimensionality; it tends to work better on low-dimensional datasets.
